A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss from Powdery Mildew in Australian Mungbean

### 2020-08-06 paper/paper.Rmd
Edit caption to be more descriptive for table 1

# Build table
PM_Mdat %>%
  filter(fungicide_ai == "tebuconazole" |
           fungicide_ai == "propiconazole") %>%
  group_by(trial_ref) %>%
  summarise(
    year = unique(year),
    location = unique(location),
    planting_date = unique(planting_date),
    first_sign_disease = unique(first_sign_disease)
  ) %>%
  arrange(year) %>%
  mutate(Research_org = c(
    rep("DAF$^{a}$", times = 4),
    rep("NGA$^{b}$", times = 4),
    rep("DAF$^{a}$", times = 4),
    rep("USQ$^{c}$", times = 5)
  )) %>%
  rename(
    `Unique Trial Reference` = trial_ref,
    Year = year,
    Location = location,
    `Planting Date` = planting_date,
    `Date First Sign` = first_sign_disease,
    `Research Organisation` = Research_org
  ) %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    escape = FALSE,
    caption = "Description of fungicide application experiments."
  ) %>%
  kable_styling() %>%
  footnote(
    alphabet = c(
      "Queensland Department of Agriculture, Fisheries and Forestry",
      "Northern Growers Alliance",
      "University of Southern Queensland"
    )
  )
```

>>>>

# Build table
PM_Mdat %>%
  filter(fungicide_ai == "tebuconazole" |
           fungicide_ai == "propiconazole") %>%
  group_by(trial_ref) %>%
  summarise(
    year = unique(year),
    location = unique(location),
    planting_date = unique(planting_date),
    first_sign_disease = unique(first_sign_disease)
  ) %>%
  arrange(year) %>%
  mutate(Research_org = c(
    rep("DAF$^{a}$", times = 4),
    rep("NGA$^{b}$", times = 4),
    rep("DAF$^{a}$", times = 4),
    rep("USQ$^{c}$", times = 5)
  )) %>%
  rename(
    `Unique Trial Reference` = trial_ref,
    Year = year,
    Location = location,
    `Planting Date` = planting_date,
    `Date First Sign` = first_sign_disease,
    `Research Organisation` = Research_org
  ) %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    escape = FALSE,
    caption = "Description of fungicide application trials included in meta-analysis to determine the most effective fungicide spray schedule to minimise yield loss from powdery mildew in Australian mungbean. Trials were all conducted in the Grains Research and Development (GRDC) Northern Grains Region of eastern Australia to test application timing for the best control of powdery mildew of mungbean."
  ) %>%
  kable_styling() %>%
  footnote(
    alphabet = c(
      "Queensland Department of Agriculture, Fisheries and Forestry",
      "Northern Growers Alliance",
      "University of Southern Queensland"
    )
  )
```
